Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm

### 2023-11-15 paper/SST/3-response_reviewer1.tex

% Reviewer 1
\reviewer
% Comment 1
\begin{revcomment}
  Grammatical and spelling errors are still observed. Please check and fix carefully.
\end{revcomment}
\begin{revresponse}

We apologize for our oversight regarding the grammatical and spelling errors, and we have thoroughly reviewed the manuscript and rectified them. Additionally, the manuscript has undergone revisions by a professional organization to ensure the accuracy of grammar and spelling.

### 2023-11-15 paper/SST/3-main.tex
根据 SST 提交要求简化了题目和摘要

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
\title{Determining the Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}

@@

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems (RBSs) provide a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structures that can be adapted to different battery charging and discharging strategies.
A critical system parameter known as the maximum allowable current (MAC) is pivotal to RBS operation. This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, ensuring its safety and reliability.
In this paper, a method is proposed for calculating the MAC of an arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
Using the shortest path (SP) of the battery, the greedy algorithm transforms the exhaustion of the switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithms) in the combination of the shortest paths.
This significantly enhances the efficiency with which the MAC is determined.
The directed graph model, based on an equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated using two previously published RBS structures and an additional one with a more complex structure.
The results are the same as those from the brute-force algorithm, but the proposed method significantly improves the computational efficiency, being theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches.
Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries.
\end{abstract}

>>>>

%%%%%% Title %%%%%%
% Full titles can be a maximum of 100 characters, including spaces. 
% Title Format: Use title case, capitalizing the first letter of each word, except for certain small words, such as articles and short prepositions
% \title{Using a Directed Graph Model and Greedy Algorithm to Determine the Maximum Allowable Current in a Reconfigurable Battery System}
\title{Determining Maximum Allowable Current of an RBS using a Directed Graph Model and Greedy Algorithm}

@@

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems provide a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structures that can be adapted to different battery charging and discharging strategies.
A critical system parameter known as the maximum allowable current (MAC) is pivotal to RBS operation. This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, ensuring its safety and reliability.
This paper proposes a method for calculating the MAC of an arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
Using the shortest path of the battery, the greedy algorithm transforms the exhaustion of the switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms in the combination of the shortest paths.
The directed graph model, based on an equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated using two previously published RBS structures and an additional one with a more complex structure.
The results are the same as those from the brute-force algorithm, but the proposed method significantly improves the computational efficiency, being theoretically $N_s2^{N_s-N_b}\log_{10}N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches.
Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable batteries, even in scenarios with random isolated batteries. 
\end{abstract}
